Study of Higgs plus single top production using events with a same sign dimuon at the Large Hadron Collider

### 2019-11-26 tesis_hiram/Chapter1/chapter1.tex
fixes
fix crossection
th yields
kt

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=0.3]{Chapter1/sm1.png}
    \caption[Standard Model to date]{Standard Model to date\cite{smtable}}
    \label{sm1}
  \end{figure}
\end{center}
The last group of the family are the bosons, which have either spin 1 or 0. 
There are 5 bosons: $W^{\pm}$, $Z$ with neutral charge are responsible for weak force; photon, a massless particle, is responsible for the electromagnetic force; gluons which are also massless, is related to the strong force and Higgs boson, recently discovered, is in charge of giving the property of mass to particles via the Higgs mechanism. Bosons let other particles interact, even themselves, which is shown in Figure \ref{sm}. 
The $W$,$Z$ and Higgs bosons, can interact with the most of the particles, while the gluons can only interact with quarks and with itself.
\afterpage{
	\begin{figure}[ht]
	\centering
	\includegraphics[scale=0.3]{Chapter1/sm.png}
	\caption[Particle interactions in Standard model]{Particle interactions in Standard model\cite{smi}}
	\label{sm}
\end{figure}
\clearpage}
%Those bosons act as mediators in decays and creation of complex
%partiles, as mesons and baryons.
%In case of gravity, exist a theoretical particle, called graviton, that is the fundamental particle associated with the gravitational force. In case of its existance, it should have a spin 2 and mass 0. 
%There are experiments that detect particles around the world, such as the LHC in Europe, the Fermilab in United States of America, KEK in Japan, etc. More information about the LHC will be described in the next chapters.

@@

\section{Higgs mechanism}
In the SM, mathematically the particles are described in form of fields. The SM for electroweak interactions is described as a gauge theory with a symmetry group SU(2)$\otimes$U(1)
that describes the weak and electromagnetic interactions
due to the exchange of spin 1 gauge fields($W^{\pm}$,$Z$) for the weak part and a photon for the electromagnetic part. The Higgs mechanism give bosons and fermions their mass. The lagrangian for the electroweak part of SM
\begin{align}\label{sml}
\mathcal{L_{\text{EW}}}=\mathcal{L}_\text{gauge}+\mathcal{L}_f +\mathcal{L}_\text{Higgs} + \mathcal{L}_\text{Yukawa}
\end{align}
The first term of the lagrangian refers to gauge bosons 
 \begin{align}\label{smg}
 \mathcal{L}_\text{gauge}=-\frac{1}{4}\left[F^{\mu\nu}F_{\mu\nu}\right]-\frac{1}{4}\left[\sum_{i}G^{i\mu\nu}G^i_{\mu\nu}\right]
 \end{align}
where the F and G are\footnote{$\epsilon^{ijk}$ represents the Levi-Civita tensor, where $\epsilon^{ijk}= \begin{dcases}
	+1 \quad \text{for even permutation} \\
	-1 \quad \text{for odd permutation}\\
	0 \quad \text{i=j, or j=k, or k=i } 
	\end{dcases}$.} 
\begin{align}
F^{\mu \nu}=\partial_\mu B_\nu -\partial_\nu B_\mu \\
G^{i\mu\nu}=\partial_\mu W^i_\nu -\partial_\nu W^i_\mu -g\epsilon^{ijk}W^j_\mu W^k_\nu 
\end{align}
$W^i$ (i=1,2,3) are three SU(2) gauge bosons, B is a U(1) gauge boson and $g$  is a couping constant for $W$ gauge boson. In the end, a superposition of these gauge bosons, after introducing the Higgs mechanism, become the $W^\pm$, $Z$ and $\gamma$ vector boson
\cite{ew1,ew2}. %Z bosons and photons will be formed by a combination of W and B fields.\\

@@

\begin{table}[ht]
\centering
\caption[Higgs boson production cross sections in pp collisions number of events for  35.9 fb$^{-1}$ ]{	Higgs boson production cross sections in pp collisions for $\sqrt{s}=13$TeV (in pico barn) and number of events for an integrated luminosity of 35.9 fb$^{-1}$ for Run 2  \cite{pd}}
\begin{tabular}{|c|c|c|}
\hline
Production mechanism &
$\sigma$ (picobarns pb) & Number of events \\
\hline
$gg$F & 48.93 & 1756587\\
\hline
VBF & 3.78 & 135702\\
\hline
$WH$ & 1.35 & 48465\\
\hline
$ZH$ &0.88 & 31592\\
\hline
$t\bar{t}$H & 0.50 & 18255\\
\hline
$tH$	& 0.015 & 560.39\\
\hline
\end{tabular}
\label{crt}
\end{table}

@@

\section{$tH$ production mechanism}
The production of $tH$, where a Higgs boson can be radiated
either from the top quark or from the exchanged $W$ boson in the two dominant leading order
diagrams shown in Figure \ref{newth} provides a unique opportunity to study the relative sign of the Higgs top coupling.
In practice, we do not directly measure the Yukawa couplings. Instead, modifier parameters $k_t$ and $k_V$ are introduced in the analysis to represent deviations from the Yukawa coupling values. 
In the SM, the two diagrams interfere negatively and thereby suppress the production cross section.
Any deviation from the SM coupling parameters can lead to a large enhancement of the event rate. 
In this project we consider a modified model with $k_t$=-1, which leads to a constructive interference and a $tH$ cross section more than ten times. 
 %$\kappa_t$ and $\kappa_V$ are the modifier of the coupling parameters discussed in section 1.5, where $\kappa_t$ is for the top and $\kappa_V$ for $W$ boson.

>>>>

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=0.3]{Chapter1/sm1.png}
    \caption[Standard Model to date]{List of particles in the Standard Model and their properties\cite{smtable}}
    \label{sm1}
  \end{figure}
\end{center}
The last group of the family are the bosons, which have either spin 1 or 0. 
There are 5 bosons: $W^{\pm}$, $Z$ with neutral charge are responsible for weak force; photon, a massless particle, is responsible for the electromagnetic force; gluons which are also massless, is related to the strong force and Higgs boson, recently discovered, is in charge of giving the property of mass to particles via the Higgs mechanism. Bosons let other particles interact, even themselves, which is shown in Figure \ref{sm}. 
The $W$,$Z$ and Higgs bosons, can interact with the most of the particles, while the gluons can only interact with quarks and with itself.
\afterpage{
	\begin{figure}[ht]
	\centering
	\includegraphics[scale=0.3]{Chapter1/sm.png}
	\caption[Particle interactions in Standard model]{Particle interactions in Standard model\cite{smi}}
	\label{sm}
\end{figure}
\clearpage}
%Those bosons act as mediators in decays and creation of complex
%partiles, as mesons and baryons.
%In case of gravity, exist a theoretical particle, called graviton, that is the fundamental particle associated with the gravitational force. In case of its existance, it should have a spin 2 and mass 0. 
%There are experiments that detect particles around the world, such as the LHC in Europe, the Fermilab in United States of America, KEK in Japan, etc. More information about the LHC will be described in the next chapters.

@@

\section{Higgs mechanism}
\label{sec:higgsmechanism}
In the SM, mathematically the particles are described in form of fields. The SM for electroweak interactions is described as a gauge theory with a symmetry group SU(2)$\otimes$U(1)
that describes the weak and electromagnetic interactions
due to the exchange of spin 1 gauge fields($W^{\pm}$,$Z$) for the weak part and a photon for the electromagnetic part. The Higgs mechanism give bosons and fermions their mass. The lagrangian for the electroweak part of SM
\begin{align}\label{sml}
\mathcal{L_{\text{EW}}}=\mathcal{L}_\text{gauge}+\mathcal{L}_f +\mathcal{L}_\text{Higgs} + \mathcal{L}_\text{Yukawa}
\end{align}
The first term of the lagrangian refers to gauge bosons 
 \begin{align}\label{smg}
 \mathcal{L}_\text{gauge}=-\frac{1}{4}\left[F^{\mu\nu}F_{\mu\nu}\right]-\frac{1}{4}\left[\sum_{i}G^{i\mu\nu}G^i_{\mu\nu}\right]
 \end{align}
where the F and G are\footnote{$\epsilon^{ijk}$ represents the Levi-Civita tensor, where $\epsilon^{ijk}= \begin{dcases}
	+1 \quad \text{for even permutation} \\
	-1 \quad \text{for odd permutation}\\
	0 \quad \text{i=j, or j=k, or k=i } 
	\end{dcases}$.} 
\begin{align}
F^{\mu \nu}=\partial_\mu B_\nu -\partial_\nu B_\mu \\
G^{i\mu\nu}=\partial_\mu W^i_\nu -\partial_\nu W^i_\mu -g\epsilon^{ijk}W^j_\mu W^k_\nu 
\end{align}
$W^i$ (i=1,2,3) are three SU(2) gauge bosons, B is a U(1) gauge boson and $g$  is a couping constant for $W$ gauge boson. In the end, a superposition of these gauge bosons, after introducing the Higgs mechanism, become the $W^\pm$, $Z$ and $\gamma$ vector boson
\cite{ew1,ew2}. %Z bosons and photons will be formed by a combination of W and B fields.\\

@@

\begin{table}[ht]
\centering
\caption[Higgs boson production cross sections in pp collisions number of events for  35.9 fb$^{-1}$ ]{	Higgs boson production cross sections in pp collisions for $\sqrt{s}=13$TeV (in pico barn) and number of events for an integrated luminosity of 35.9 fb$^{-1}$ for Run 2  \cite{pd}}
\begin{tabular}{|c|c|c|}
\hline
Production mechanism &
$\sigma$ (picobarns pb) & Number of events \\
\hline
$gg$F & 48.93 & 1756587\\
\hline
VBF & 3.78 & 135702\\
\hline
$WH$ & 1.35 & 48465\\
\hline
$ZH$ &0.88 & 31592\\
\hline
$t\bar{t}$H & 0.50 & 18255\\
\hline
$tH$	& 0.074 & 2655\\
\hline
\end{tabular}
\label{crt}
\end{table}

@@

\section{$tH$ production mechanism}
The production of $tH$, where a Higgs boson can be radiated
either from the top quark or from the exchanged $W$ boson in the two dominant leading order
diagrams shown in Figure \ref{newth} provides a unique opportunity to study the relative sign of the Higgs top coupling.
In practice, we do not directly measure the Yukawa couplings.
Instead, modifier parameters $k_t$ and $k_V$ are introduced in the analysis to represent deviations from the Yukawa coupling values described in Section~\ref{sec:higgsmechanism}. 
In the SM, the two diagrams interfere negatively and thereby suppress the production cross section.
Any deviation from the SM coupling parameters can lead to a large enhancement of the event rate. 
In this project we consider a modified model with $k_t$=-1, which leads to a constructive interference and a $tH$ cross section more than ten times. 
 %$\kappa_t$ and $\kappa_V$ are the modifier of the coupling parameters discussed in section 1.5, where $\kappa_t$ is for the top and $\kappa_V$ for $W$ boson.
